The Rapid Cycleway Prioritisation Tool

### 2020-06-17 rapid-slides.Rmd
Final update to slides, heads-up @joeytalbot

Every city in England

## Results

@@

- Consultation on the Torrington Place / Tavistock Place 'pop-up' cycleway from [Cambden.gov.uk](https://www.camden.gov.uk/documents/20142/3452947/Consultation+leaflet+FINAL.pdf/f628d6e8-c47b-82f1-cb40-8e24db78bea6)

>>>>

@@

- Consultation on the Torrington Place / Tavistock Place 'pop-up' cycleway from [Camden.gov.uk](https://www.camden.gov.uk/documents/20142/3452947/Consultation+leaflet+FINAL.pdf/f628d6e8-c47b-82f1-cb40-8e24db78bea6)
